Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID

### 2024-01-24 outputs/paper/paper.qmd
final paper updated upload

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2018
#| fig-cap: Total 2018 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2019
#| fig-cap: Total 2019 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2020
#| fig-cap: Total 2020 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2021
#| fig-cap: Total 2021 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2022
#| fig-cap: Total 2022 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2018
#| fig-cap: Total 2018 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2019
#| fig-cap: Total 2019 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2020
#| fig-cap: Total 2020 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2021
#| fig-cap: Total 2021 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2022
#| fig-cap: Total 2022 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward

>>>>

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2018
#| fig-cap: Total 2018 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2019
#| fig-cap: Total 2019 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2020
#| fig-cap: Total 2020 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2021
#| fig-cap: Total 2021 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2022
#| fig-cap: Total 2022 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2018
#| fig-cap: Total 2018 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2019
#| fig-cap: Total 2019 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2020
#| fig-cap: Total 2020 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2021
#| fig-cap: Total 2021 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2022
#| fig-cap: Total 2022 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
